Tree-structured neural networks revisited

### 2016-03-01 writing/hard_stack_paper/paper.tex
Results table fleshing out.

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Trained params.    &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{\bf Non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                 &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{\bf Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                &   98.8   &   81.4       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\midrule
\multicolumn{4}{c}{\bf Previous NN results with attention}\\
\midrule
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\midrule
\multicolumn{4}{c}{\bf New results}\\
\midrule150d LSTM RNN           & ?                  &   ?      &   81?       \\
150d TB TreeLSTM    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, sequence-based attn.        
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, tree-based attn.            
                        & ?                  &   ?      &   \textbf{82?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \todo{Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

>>>>

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Trained params.    &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                 &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous NN results without attention}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m               &   83.4   &   82.1       \\
\todo{[SB] Import baselines from page}  
                        & ?                  &   ?      &   81?       \\
\midrule
\multicolumn{4}{c}{Previous NN results with attention}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long} (1.4m params) 92.3    89.1

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule150d LSTM RNN           & ?                  &   ?      &   81?       \\
150d TB TreeLSTM    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, sequence-based attn.        
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, tree-based attn.            
                        & ?                  &   ?      &   \textbf{82?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \todo{Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}
